### 2014-02-12 tex/pseudo-code.tex
Added

\section{Pseudo-code}

The presentation assumes a purely syntactic semantics for a CEKS
machine for a Java-like language \cite{saints-MS}. The machine state
for the semantics consists of a (C)ontrol string representing the
expression being evaluated, an (E)nvironment for local variables, a
(K)ontinuation for what is to be executed next, and a (S)tore for the
heap. This paper only defines salient features of the machine relevant to understanding the new algorithm.
\begin{itemize}
\item $n$ are numbers, and the set of all positive natural numbers is $\mathbb{N}^+$.
\item $x$ is a variable, and the set of all variables is $X$.
\item $f$ is a field name in an object, and the set of all field names is $F$.
\item $v$ is a value, and the set of all values is $V$. A value can only be a reference. 
\item $\eta : X \rightarrow V$ is an environment
\item $h$ is a heap represented as a bipartite graph (see below).
\item $k$ is a continuation to resolve evaluation order and return points from calls. Of particular interest are the continuations for completion (\texttt{ret}), ...
\item $e$ is an expression. Expressions can be values $v$, sequencing
  ($(begin\ e\ \ldots)$), field access ($(x.f)$ or $(x.f := e)$), and
  other constructs to be defined soon,...
\item $\mu$ is the text that defines classes and methods.
\item $P$ is a program $(\mu, (C m))$ where $C$ is a class defined in
  $\mu$ and $m$ is a method in that class.
\item $s = (\mu\ h\ \eta\ e\ k)$ is a machine state.
\item $(\mu\ h^\prime\ \eta^\prime\ e^\prime\ k^\prime) =
  \mathrm{execute}(\mu, h, \eta, e, k)$ is a function that returns a
  state by evaluating the expression.
\end{itemize}

>>>>

\section{Pseudo-code}
The presentation assumes a CEKS machine for a Java-like language
(mostly a syntactic machine) \cite{saints-MS}. The machine state for
the semantics consists of a (C)ontrol string representing the
expression being evaluated, an (E)nvironment for local variables, a
(K)ontinuation for what is to be executed next, and a (S)tore for the
heap. This paper only defines salient features of the machine relevant
to understanding the new algorithm.

The language is defined as in the following figure.
\input{grammar}

%\item $n$ are numbers, and the set of all positive natural numbers is $\mathbb{N}^+$.
\begin{itemize}
\item $x \in X$ is a variable
\item $f\in F$ is a field name in an object
\item $r\in V$ is a reference
\item $e$ is an expression.
  \begin{itemize}
  \item $v$
  \item $x$
  \item $(e\ \$\ f)$
  \item $(x\ := e)$
  \item
  \end{itemize} Expressions can be values $v$, sequencing
  ($(begin\ e\ \ldots)$), field access ($(x.f)$ or $(x.f := e)$), and
  other constructs to be defined soon,...
\item $\mu$ is the text that defines classes and methods.
\item $P$ is a program $(\mu, (C m))$ where $C$ is a class defined in
  $\mu$ and $m$ is a method in that class.
\item $(L,R)$ represent the heap and form a bipartite graph (see below).
\item $\eta : X \rightarrow V$ is an environment
\item $k$ is a continuation to resolve evaluation order and return points from calls
\begin{itemize}
\item $\mathtt{end}$: nothing comes next
\item $(*\ \$\ f \rightarrow k)$: access field $f$ once expression is reduced to a reference.
\end{itemize}
\item $s = (\mu\ h\ \eta\ e\ k)$ is a machine state.
\item $(\mu\ h^\prime\ \eta^\prime\ e^\prime\ k^\prime) =
  \mathrm{execute}(\mu, h, \eta, e, k)$ is a function that returns a
  state by evaluating the expression.
\end{itemize}
